Learning with Misspecified Models:\\ overconfidence and stereotypes

### 2023-09-29 Slides/overconfident_beliefs/Sept23_choaching.tex
slides setup

\usepackage{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{theorem}
\usepackage{natbib}
\usepackage{mathtools}
\usepackage{cite}
\usepackage{natbib}
\usepackage{setspace}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage{array}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[normalem]{ulem}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{calc}
\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{wrapfig}
\usepackage{adjustbox}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage[table]{xcolor}

\title{Models of Belief Updating:\\ The Case of Overconfidence}
\author{Jimena Galindo}

@@

\begin{frame}{Motivation}
    We often observe beliefs and behaviors that are inconsistent with the fully Bayesian benchmark:\\
    \bigskip
    \begin{itemize} 
        \item Overconfidence  
        \item Polarization 
    \end{itemize}

    \bigskip
    Recent theoretical literature has sought to explain these phenomena (and others) with the notion of \bf{Misspecified Mental Models}
\end{frame}

\begin{frame}{Motivation}
    We often observe beliefs and behaviors that are inconsistent with the fully Bayesian benchmark:\\
    \bigskip
    \begin{itemize} 
        \item Overconfidence \textbf{(today)}  
        \item Polarization \textbf{(next time)}
    \end{itemize}

    \bigskip
    Recent theoretical literature has sought to explain these phenomena (and others) with the notion of \bf{Misspecified Mental Models}
\end{frame}

A prior on unknown parameters/states and an updating procedure\\
\bigskip
\begin{itemize}
    \item Bayesian 
    \item Dogmatic 
    \item Motivated Beliefs
\end{itemize}

@@

\begin{frame}{Overconfidence}
    Belief that my type is higher than it truly is (``overestimation'' as in Moore and Healy, 2008)\\
    \bigskip

    Overconfidence seems to be persistent in various settings. Ultimately it leads to sub-optimal choices:
    \begin{itemize} 
        \item Excess entry of entrepreneurs (Camerer and Lovallo, 1999)
        \item Suboptimal genetic testing (Oster et al. 2013)
        \item  Workers overestimate their productivity (Hoffman and Burks, 2020)
    \end{itemize}

\begin{frame}{An Example}
    An entrepreneur has \textbf{unknown intrinsic ability} $\theta^*$ and chooses a level of effort $e\geq 0.$ \\
    \bigskip
    Effort and ability are transformed into output at an exogenous and \textbf{unknown rate} $\omega.$\\
    \bigskip 
    An overconfident entrepreneur believes he is of type $\hat\theta>\theta^*$\\
    \bigskip

    The entrepreneur wants to maximize their utility\\
        $$y = (\theta^* + e)\omega-\frac{1}{2}e^2 +\varepsilon$$\\
    \pause
    \bigskip
    Regardless of their own type (or their beliefs about it), they should choose $e^*(\omega)=\omega$\\
\end{frame}

@@

    \begin{itemize}
        \item Choosing $\hat{e}$ and $\hat{e}+1$ over multiple periods allows identification of $\omega$\\
        \bigskip
        \item Once $\omega$ is known, $\theta$ can be backed out\\
     \end{itemize}
    \bigskip
    How come people don't learn the true $\theta$?
\end{frame}

\begin{frame}{The Literature}
Settings with two or more unknowns allow for different explanations of the bias:\\
\bigskip
\begin{enumerate}
\item Self-defeating equilibrium (Heidhues et al., 2018): 
    \begin{itemize}
        \item Bayesian on $\omega$
        \item Dogmatic about $\theta$

@@

\begin{frame}{The Research Questions}
    We know people fall somewhere between Bayesian Learning and the very extreme Heidhues et al. setting.\\
    \bigskip
    \begin{itemize}
        \item To what extent do the different theories explain the data?\\
        \begin{itemize}
            \item Is there heterogeneity in the way people update beliefs?\\
        \end{itemize}
    \end{itemize}
    \pause
    \bigskip
    Misspecified mental models lead to incorrect beliefs even in settings where there are no ego-relevant parameters
    \bigskip
    \begin{itemize}
        \item How do the models perform in a setting with two parameters that are NOT ego-relevant?\\
    \end{itemize}
\end{frame}

\begin{frame}{Roadmap}
    \begin{enumerate}
        \item Theory 1 --- Further Motivation\\
        \bigskip
        \item Theory 2\\
        \bigskip
        \item Theory 3\\
        \bigskip
        \item Unifying framework\\
        \bigskip
        \item Experimental Design
    \end{enumerate}
\end{frame}

@@

$\omega$ is drawn from density $g_0$ with $\omega^*=E_{g_0}(\omega).$\\
\bigskip
The entrepreneur's true ability is $\theta^*$, they believe with certainty that it is $\hat\theta>\theta^*.$ \\
\bigskip
At $t=0$, the entrepreneur has the prior $g_0.$\\
\bigskip
They correctly choose $e_0 = \omega^*.$\\
\bigskip
\pause
Suppose they don't update their beliefs or their choice for a long time.
\end{frame}

@@

\begin{frame}{Bayesian updating}
    Updating choices every period (myopically) the belief will drift even further:\\
    \bigskip
    A lower choice of $e$ still gives a lower output than expected. \\
    \bigskip
    So $\omega_{t+1}$ must be lower than they believed in period $t$.\\
    \bigskip
    Heidhues et al. show that this process converges to a belief $\omega_\infty<\omega_1<\omega^*.$\\
    \bigskip
    The result is symmetric for underconfident subjects.

@@

\begin{frame}{In the Lab}
\label{Figure1}

Götte and Kozakiewicz (2022) test the predictions in a lab experiment:

\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figures/GK_experiment.png}
\end{figure}
    \hyperlink{Other Figures}{\beamerbutton{Other Figures}}

\begin{frame}{Results}
    Biased updating in the same direction as the theoretical predictions.\\
    \bigskip
    The bias is not as large as the theory predicts.\\
    \bigskip
    Some agents do update their belief of $\theta$ in the right direction.\\
\end{frame}

@@

\begin{frame}{The Setting}
    Same as HKS but with finite $\Omega$ and finite $A$\\
    \bigskip
    Now the entrepreneur is willing to switch to an alternative level of ability $\theta'$ (assume $\theta' = \theta^*$).\\
    \bigskip
    Instead of updating $P[\theta]$ every period, they perform a Bayesian hypothesis test:\\
    \bigskip
    Adopt model $\theta'$ at time t iff \\
    $$\frac{\ell_t (\theta')}{\ell_t(\theta)}>\alpha\geq1$$

@@

    The self-defeating trap is difficult to escape when the entrepreneur is overconfident.\\
    \bigskip
    Underconfident agents escape the trap at a higher rate than overconfident and learn the true parameter.\\
    \bigskip
    Explains why underconfidence is less prevalent in the data.\\
    \bigskip
    Overconfident agents can escape the trap if their prior is not too ``tight'' around a self confirming equilibrium.

@@

\begin{frame}{Theory 3: Motivated Beliefs}
    \Large\textbf{Optimal Expectations}\\
    (Brunnermeier and Parker, 2005)\\
    \bigskip
    \Large\textbf{What to blame? Self-serving attribution bias with
multi-dimensional uncertainty}\\
    (Coutts et al., 2022 wp)
\end{frame}

\begin{frame}{The Setting}
    A fixed effort $e$, $\theta \in \{\theta_H, \theta_L\}$ and $\omega \in \{\omega_H, \omega_L\}$ generate binary signals (success/failure)\\
    \bigskip
    After a success the agent updates their belief about $\theta$ with distortions $\gamma_\theta$ and $\gamma_\omega$, $p_{t+1}(\theta_H|success)$ is given by:\\
    \begin{center}
        \small
        $\frac{\gamma^s_\theta\gamma^s_\omega\pi_t(\theta_H) g_t(\omega_H) q_t(\theta_H, \omega_H) + \gamma^s_\theta\pi_t(\theta_H) g_t(\omega_L) q_t(\theta_H, \omega_L)}{\gamma^s_\theta\gamma^s_\omega\pi_t(\theta_H) g_t(\omega_H) q_t(\theta_H, \omega_H) + \gamma^s_\theta\pi_t(\theta_H) g_t(\omega_L) q_t(\theta_H, \omega_L) + \gamma^s_\omega\pi_t(\theta_L) g_t(\omega_H) q_t(\theta_L, \omega_H) + \pi_t(\theta_L) g_t(\omega_L) q_t(\theta_L, \omega_L)}$\\
    \end{center}
    \bigskip
    with $q_t(\theta, \omega):=Pr[\text{success}|\theta, \omega]$ increasing in $\omega$ and $\theta$
\end{frame}

\begin{frame}{Predictions and Evidence (Coutts et al. 2022)}
    Prediction: Even unbiased agents will overweight $\theta_H$ after a success and end up being biased.\\
    \bigskip
    Experiment: Evidence of biased updating when $\theta$ is ego-relevant.\\
    \bigskip
    The framework does not allow direct comparisons with the other two theoretical predictions.\\
    \bigskip
    It gives an alternative rationalization for the persistence of overconfidence.

@@

\begin{frame}{A framework where we can compare}

@@

\begin{frame}{Example: Dogmatic Modeler}
\begin{itemize}
    \item Theory 1: for an entrepreneur who believes he is $\theta_H$
    \end{itemize}
    \bigskip
    \begin{enumerate}
        \item Chooses $e_H$ and is disappointed $\rightarrow$ adjust belief about $\omega$ downward\\
        \bigskip
        \item Eventually chooses $e_M$ and is disappointed as well $\rightarrow$ adjust belief about $\omega$\\
        \bigskip
        \item Eventually chooses $e_L$ and falls into a self-confirming equilibrium
    \end{enumerate}

@@

\begin{frame}{Dogmatic Overconfident}
    \begin{figure}
        \centering
        \includegraphics[trim=0 20 0 0, clip]{figures/dogmatic.png}
        \caption{$\theta^*=\theta_M$, $\hat\theta=\theta_H$, $\omega^*=\omega_M$}
    \end{figure}
\end{frame}

@@

\begin{frame}{Switcher Overconfident}
    \begin{figure}
        \centering
        \includegraphics{figures/switch.png}
        \caption{$\theta^*=\theta_M$, $\hat\theta=\theta_H$, $\omega^*=\omega_M$, $\alpha= 1.1$}
    \end{figure}
\end{frame}

@@

\begin{frame}{Dogmatic Overconfident}
    \begin{figure}
        \centering
        \includegraphics{figures/SS.png}
        \caption{$\gamma^s_\theta=1.2$, $\gamma^s_\omega = .8$}
    \end{figure}
\end{frame}

\begin{frame}{The Simulation}
\label{Figure2}
    \begin{figure}
    \centering
    \includegraphics[scale=0.43]{figures/all_1_1.png}
\end{figure}

\hyperlink{WorstCase}{\beamerreturnbutton{Other Cases}}

@@

\begin{frame}{The Experiment:}
Brief Questionnaire: Age, Gender, Nationality, Major\\
\bigskip
Part 1: Set Types\\
\bigskip
\begin{itemize}
    \item Quiz: Answer as many questions as you can in 2 minutes:\\
    \begin{itemize}
        \item Math, Verbal, Pop-Culture, Science, Us Geography, Sports and Videogames\\
    \end{itemize}
    \bigskip
    \item How many questions do you think you answered correctly in each quiz?\\
    \begin{itemize}
        \item[o] Bin1, Bin2, Bin3
    \end{itemize}
\end{itemize}

@@

\begin{frame}{The Experiment: Ego-relevant condition}
Belief updating and effort choice (One topic at a time)\\
\bigskip
\begin{itemize}
    \item Choose an effort
    \item Receive a signal realization
\end{itemize}
\bigskip
25 rounds per topic

@@

\begin{frame}{The Experiment: Ego-irrelevant condition}

Observe the characteristics of a participant. 
\begin{itemize}
    \item ``What score do you think this participant got in the (topic) quiz?'' 
    \item Bin1, Bin2, Bin3 
\end{itemize}

Belief updating and effort choice\\
\bigskip
\begin{itemize}
    \item Choose an effort
    \item Receive a signal realization
    \begin{itemize}
        \item[o] The DGP is that of the observed participant
    \end{itemize}
\end{itemize}
\bigskip
25 rounds (per topic/participant)

@@

@@

\begin{frame}{Götte and Kozakiewicz (2022) }
\label{Other Figures}
    \begin{figure}
    \centering
    \includegraphics[scale=0.45]{figures/GK_under-unbiased.png}
\end{figure}

\hyperlink{Figure1}{\beamerreturnbutton{Back}}

\begin{frame}{A Bad Case}
\label{WorstCase}
    \begin{figure}
    \centering
    \includegraphics[scale=0.4]{figures/all_2_2.png}
\end{figure}

\hyperlink{Figure2}{\beamerreturnbutton{Back}}

>>>>

\usepackage{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{theorem}
\usepackage{natbib}
\usepackage{mathtools}
\usepackage{cite}
\usepackage{natbib}
\usepackage{setspace}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage{array}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[normalem]{ulem}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{calc}
\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{wrapfig}
\usepackage{adjustbox}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage[table]{xcolor}
\usepackage{xcolor}

\title{Learning with Misspecified Models:\\  overconfidence and stereotypes}
\author{Jimena Galindo}

@@

\begin{frame}{Motivation}
    Updating beliefs is a difficult task\\
    \bigskip
    Mounting evidence of biases\\
\documentclass[aspectratio=169]{beamer}

\usepackage{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{theorem}
\usepackage{natbib}
\usepackage{mathtools}
\usepackage{cite}
\usepackage{natbib}
\usepackage{setspace}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage{array}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[normalem]{ulem}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{calc}
\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{wrapfig}
\usepackage{adjustbox}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage[table]{xcolor}
\usepackage{xcolor}

\title{Learning with Misspecified Models:\\  overconfidence and stereotypes}
\author{Jimena Galindo}

\begin{frame}{Motivation}
    Updating beliefs is a difficult task\\
    \bigskip
    Mounting evidence of biases\\
\documentclass[aspectratio=169]{beamer}

\usepackage{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{theorem}
\usepackage{natbib}
\usepackage{mathtools}
\usepackage{cite}
\usepackage{natbib}
\usepackage{setspace}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage{array}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[normalem]{ulem}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{calc}
\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{wrapfig}
\usepackage{adjustbox}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage[table]{xcolor}
\usepackage{xcolor}

\title{Learning with Misspecified Models:\\  overconfidence and stereotypes}
\author{Jimena Galindo}

\begin{frame}{Motivation}
    Updating beliefs is a difficult task\\
    \bigskip
    Mounting evidence of biases\\
    \bigskip
    Economic theory developed models that rationalize biased behaviors
\end{frame}

\begin{frame}{Prevalence of Overconfidence}

   \textbf{OVERCONFIDENCE}: Belief that my type is higher than it truly is (``overestimation'' as in Moore and Healy, 2008)\\
    \bigskip

    Overconfidence seems to be persistent in various settings. Ultimately it leads to sub-optimal choices:
    \begin{itemize} 
        \item Excess entry of entrepreneurs (Camerer and Lovallo, 1999)
        \item Suboptimal genetic testing and healthcare (Oster et al. 2013)
        \item  Workers overestimate their productivity (Hoffman and Burks, 2020)
    \end{itemize}

@@

\begin{frame}{An Example}
    A student has \textbf{unknown intrinsic ability} $\theta^*$ and chooses a level of effort $e\geq 0$. \\
    \bigskip
    Effort and ability are transformed into a noisy output at an exogenous and \textbf{unknown rate} $\omega.$\\
    \bigskip 
    An overconfident student believes he is of type $\hat\theta>\theta^*$\\
    \bigskip

    And wants to maximize utility\\
        $$y = (\theta^* + e)\omega-\frac{1}{2}e^2 +\varepsilon$$\\
    \pause
    \bigskip
   {\textbf{Regardless of their own type, they should choose $e^*(\omega)=\omega$\\}}
\end{frame}

@@

    \begin{itemize}
        \item Choosing $\hat{e}$ and $\hat{e}+1$ over multiple periods allows identification of $\omega$\\
        \bigskip
        \item Once $\omega$ is known, $\theta$ can be backed out\\
     \end{itemize}
    \bigskip
    How come people don't learn their true type and don't choose the optimal effort?
\end{frame}

A prior belief over parameters/states/types and an updating procedure\\
\bigskip
\begin{itemize}
    \item Bayesian 
    \item Dogmatic 
    \item Motivated Beliefs/Self-attribution
\end{itemize}
\end{frame}

\begin{frame}{Research Questions}
    To what extent do the different theories explain observed behavior?\\
    \begin{itemize}
        \item Do we observe heterogeneity in the use of mental models?
    \end{itemize}
    \bigskip
    Is ego-relevance of the type a key feature for the misspecification?
    \begin{itemize}
        \item Can the same theories be used to explain the prevalence of stereotypes?
    \end{itemize}
\end{frame}

\begin{frame}{Road-map}
    \begin{enumerate}
        \item Three Theories of Overconfidence\\
        \bigskip
        \item Mechanisms and Predictions\\
        \bigskip
        \item Unifying Framework\\
        \bigskip
        \item Experimental Design\\
        \bigskip
        \item Results (coming soon)
    \end{enumerate}
\end{frame}

\begin{frame}{The Theories}
Settings with two or more unknowns allow for different explanations of the bias:\\
\bigskip
\begin{enumerate}
\item Self-defeating equilibrium (Heidhues et al., 2018): 
    \begin{itemize}
        \item Bayesian on $\omega$
        \item Dogmatic about $\theta$

@@

@@

The student's true ability is $\theta^*$, they believe with certainty that it is $\hat\theta>\theta^*.$ \\
\bigskip
The rate $\omega$ is drawn from density $g_0$ with $\omega^*=E_{g_0}(\omega).$\\

\bigskip
At $t=0$, the student has the prior $g_0.$\\
\bigskip
They correctly choose $e_0 = \omega^*.$\\
\bigskip
\pause
\textbf{Suppose they don't update their beliefs or their choice for a number of periods.}
\end{frame}

@@

\begin{frame}{Updating the Beliefs}
    Updating choices every period (myopically) the belief will drift even further:\\
    \bigskip
    A lower choice of $e$ still gives a lower output than expected. \\
    \bigskip
    So $\omega_{t+1}$ must be lower than they believed in period $t$.\\
    \bigskip
    \textbf{Prediction:} convergence to a self-confirming equilibrium with $\omega_\infty<\omega_1<\omega^*.$\\
    \bigskip
    The result is symmetric for underconfident subjects.

@@

@@

\begin{frame}{The Setting}
    Same as HKS but with finite $\Omega$ and finite $A$\\
    \bigskip
    Now the entrepreneur is willing to switch to an alternative level of ability $\theta'$ (assume $\theta' = \theta^*$).\\
    \bigskip
    Instead of updating $P[\theta]$ every period, they perform a Bayesian hypothesis test:\\
    \bigskip
    Adopt model $\theta'$ at time t iff \\
    $$\frac{\ell_t (\theta')}{\ell_t(\hat{\theta})}>\alpha\geq1$$

@@

    \textbf{Prediction:} Misspecified agents escape the trap as long as their prior is not too ``tight'' around a self-confirming equilibrium.

@@

\begin{frame}{Theory 3: Motivated Beliefs}

    \Large\textbf{Errors in probabilistic reasoning and judgment biases}\\
    (Benjamin, 2019)\\

@@

\begin{frame}{The Setting}
    Fixed effort $e$, $\theta \in \{\theta_H, \theta_L\}$ and $\omega \in \{\omega_H, \omega_L\}$ generate binary signals (\textbf{s}/\textbf{f})\\
    \bigskip
    After a signal realization $m$, the agent updates their belief about $\theta$ with distortions $c_m^\theta$ and $c_m^\omega$, so that:\\

        $$\frac{p_{t+1}[\theta_H]}{p_{t+1}[\theta_L]} = \left(\frac{p[\text{m}|\theta_H]}{p[\text{m}|\theta_L]}\right)^{c_m^\theta}\frac{p_t[\theta_H]}{p_t[\theta_L]}$$

    and
        $$\frac{p_{t+1}[\omega_H]}{p_{t+1}[\omega_L]} = \left(\frac{p[\text{m}|\omega_H]}{p[\text{m}|\omega_L]}\right)^{c_m^\omega}\frac{p_t[\omega_H]}{p_t[\omega_L]}$$

    \bigskip
    The agent suffers from self-attribution bias if $c_s^\theta >c_f^\theta$ and $c_s^\omega < c_f^\omega$.
\end{frame}

\begin{frame}{Predictions}
    \textbf{Prediction:} Even unbiased agents will overweight $\theta_H$ after a success and end up being biased.\\
    \bigskip
    When $c^\theta = c^\omega = 1$, the updating procedure coincides with the unbiased Bayesian.\\

    \bigskip
    The framework does not allow direct comparisons with the other two theories.\\

\begin{frame}{A Unifying Framework}

@@

\begin{frame}{Example: Dogmatic Modeler}
\begin{itemize}
    \item Theory 1: for a student who believes he is $\theta_H$
    \end{itemize}
    \bigskip
    \begin{enumerate}
        \item Chooses $e_H$ and is disappointed $\rightarrow$ adjust belief about $\omega$ downward\\
        \bigskip
        \item Eventually chooses $e_M$ and is disappointed as well $\rightarrow$ adjust belief about $\omega$\\
        \bigskip
        \item Eventually chooses $e_L$ and falls into a self-confirming equilibrium
    \end{enumerate}

@@

\begin{frame}{Dogmatic Overconfident}
    \begin{figure}
        \centering
        \includegraphics[scale=.5]{figures2/dogmatic_over_11.png}
        \caption{$\theta^*=\theta_M$, $\hat\theta=\theta_H$, $\omega^*=\omega_M$}
    \end{figure}
\end{frame}

@@

\begin{frame}{Switcher Overconfident}
    \begin{figure}
        \centering
        \includegraphics[scale=.5]{figures2/switcher_over_11.png}
        \caption{$\theta^*=\theta_M$, $\hat\theta=\theta_H$, $\omega^*=\omega_M$, $\alpha= 1.1$}
    \end{figure}
\end{frame}

@@

\begin{frame}{Self-Serving Bias}
    \begin{figure}
        \centering
        \includegraphics[scale=.5]{figures2/self-serving_11.png}

    \end{figure}
\end{frame}

\begin{frame}{The Simulation}
\label{Figure2}
    \begin{figure}
    \centering
    \includegraphics[scale=0.2]{figures2/all_11.png}
\end{figure}

@@

\begin{frame}{The Experiment:}

Part 1: Set Types\\
\bigskip
\begin{itemize}
    \item Quiz: Answer as many questions as you can in 2 minutes:\\
    \begin{itemize}
        \item Math, Verbal, Pop-Culture, Science, Us Geography, Sports and Video games\\
    \end{itemize}
    \bigskip
    \item How many questions do you think you answered correctly in each quiz?\\
    \begin{itemize}
        \item[o] Bin1, Bin2, Bin3
    \end{itemize}
\end{itemize}

@@

\begin{frame}{The Experiment: Ego-relevant condition}
Belief updating and effort choice (One topic at a time)\\
\bigskip
\begin{itemize}
    \item Choose an effort
    \item Receive a sample of 10 signal realizations
\end{itemize}
\bigskip
11 rounds per topic

@@

\begin{frame}{The Experiment: Stereotype condition}

Observe the characteristics of a participant (Gender, US National or not). \\
\begin{itemize}
    \item ``What score do you think this participant got in the (topic) quiz?'' \\
    \item Bin1, Bin2, Bin3 \\
\end{itemize}
\bigskip
Belief updating and effort choice\\

\begin{itemize}
    \item Choose an effort
    \item Receive a signal realization
    \begin{itemize}
        \item[o] The DGP is that of the observed participant
    \end{itemize}
\end{itemize}
\bigskip
11 rounds (per topic/participant)

@@

\begin{frame}{Screen}
    \begin{figure}
        \centering
        \includegraphics[scale=.4]{figures2/screen1.png}
    \end{figure}
\end{frame}

\begin{frame}{Screen}
    \begin{figure}
        \centering
        \includegraphics[scale=.4]{figures2/screen2.png}
    \end{figure}
\end{frame}

@@
